```{r compile, eval=FALSE, include=FALSE}
library(knitr); system.time(knit2html('analyseeval.Rmd'))
```

```{r setOpts}
opts_chunk$set(fig.width=12, fig.height=8)
opts_chunk$set(out.width='\\textwidth')
opts_knit$set(width=140)

```

```{r loadLibs}
# install.packages("data.table")
library(data.table)
library(dplyr)
library(reshape2)
library(ggplot2)
library(GGally)

```

```{r loadData, include=FALSE}
# Load data
params <- list(num.methods=4, num.seeds=48, max.iters=7)
load.stats <- function(stats.name, key) {
    filename <- sprintf(
        "stats/stats-%s-%d-%05d-%04d.csv.gz",
        stats.name, params$num.methods, params$num.seeds, params$max.iters)
    return(data.table(read.csv(gzfile(filename)), key=key))
}
seed   <- load.stats("seed"  , key=c("seedidx"))
iter   <- load.stats("iter"  , key=c("seedidx", "iteration"))
method <- load.stats("method", key=c("seedidx", "iteration", "method"))
```

Examine the three data frames and join into one "full" data frame.
```{r examineData}
# What are the seed-level attributes?
colnames(seed)
# What are the iteration-level attributes?
colnames(iter)
# What are the method-level attributes?
colnames(method)
# Join into one data frame
full <- seed %>% inner_join(iter) %>% inner_join(method)
dim(full)
sapply(full, class)
method.names <- levels(method$method)
method.names
sample_n(full, 10)

```

Check how accurate our Z estimates are
```{r checkZestimates}
(   full
    %>% filter(iteration > 1)
    %>% group_by(method, W)
    %>% summarise(
            mean=mean(Znsumestimate / Znsumtrue),
            var=var(Znsumestimate / Znsumtrue))
)
facet.width = facet_wrap(~ W)
(   ggplot(
        full %>% filter(iteration > 1),
        aes(x=method, y=Znsumestimate / Znsumtrue))
    + scale_y_log10()
    + geom_boxplot()
    + facet.width
    + coord_cartesian(ylim=c(.1, 10.))
)

```

Compare the different PWM distance metrics
```{r compareDistMetrics}
dist.metrics <- c(
    "frobeniusdist", "maxdist", "absdist", "euclideandist"
    # , "KLtrueestimate", "KLestimatetrue"  # Can be inf or NA
)
# full[,dist.metrics]
ggpairs(
    full,
    columns=dist.metrics,
    axisLabels="show",
    diag=list(continuous="density")
)

```

Check how close the estimated PWMs are to the truth
```{r compareMethodPWMestimates}
distlims = c(1e-3, 10)
distxcoords = coord_cartesian(xlim=distlims)
distycoords = coord_cartesian(ylim=distlims)
distxycoords = coord_cartesian(xlim=distlims, ylim=distlims)
ggplot(full, aes(x=absdist / W, color=method)) +
    geom_density() +
    scale_x_log10() +
    distxcoords

```

Investigate if directionality of KL has much effect
```{r KLdirectionality}
full.with.KL <- full %>% filter(! is.na(KLestimatetrue), ! is.na(KLtrueestimate))
alpha <- .3  # Transparency
ggplot(
    full.with.KL,
    aes(x=KLtrueestimate, y=KLestimatetrue, color=method)) +
    geom_point(alpha=alpha) +
    scale_x_log10() + scale_y_log10()

```

Does number of samples correlate with PWM accuracy?
```{r samplesVsAccuracy}
model <- lm(absdist / W ~ numsamples + factor(method), data=full)
(   ggplot(
        full,
        aes(x=numsamples, y=absdist / W, color=method))
    + geom_point(alpha=alpha)
    + scale_x_log10() + scale_y_log10()
    + distycoords
    + stat_smooth(method="lm")
)

```

How does the iteration affect the accuracy of the PWM?
```{r iterationVsAccuracy}
ggplot(
    full,
    aes(x=factor(iteration), y=absdist / W, color=method)) +
    geom_boxplot(outlier.size=1) +
    scale_y_log10() + distycoords

```

Get the distance for each method
```{r methodDists}
distance <- (full
    # %>% filter(iteration > 2)
    %>% group_by(seedidx, iteration)
    %>% select(seedidx, iteration, method, absdist, W)
    %>% mutate(absdistperbase=absdist / W)
    %>% dcast(seedidx + iteration + W ~ method, value.var="absdistperbase")
)
head(distance)
ggpairs(
    distance,
    columns=method.names,
    axisLabels="show",
    diag=list(continuous="density"),
)
```

